\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\newcommand{\CommaPunct}{\mathpunct{\raisebox{0.5ex}{,}}}
\begin{document}
\title{ECE108 Assignment3} \author{Yi Fan Yu yf3yu@edu.uwaterloo.ca} \date{\today}

\maketitle

\pagenumbering{arabic}
\tableofcontents
\newpage
\renewcommand\thesubsection{\alph{subsection}}
\section{Rolling Dice}
\subsection{Dicerolling1,2,3,4,5,6}
How many times will the sequence 1,2,3,4,5,6 occur?  What is the
probability of this occurring?\\
\bigskip\\
well if $n \leq 6$, there is 0 chance of any sequence occuring\\
if $n = 6$, there is 1 occurence which means $\frac{1}{6^{6}}$ chance\\
if $n \geq 6$,there are 
  \[(n-5)*6^{n-5}\text{occurences}\]
  which leads to a probability of occurence to
  \[\frac{(n-5)*6^{n-5}}{6^{n}}\]

\subsection{DicerollingA,B,C}
How many times will the sum of the number of 1's and 2's equal the
sum of the number of 3's, 4's, 5's and 6's?  What is the probability
of this occurring?
let's say\\
\[ 1 \& 2 \mapsto A\]
\[ 3 \& 4 \mapsto B\]
\[ 5 \& 6 \mapsto C\]
$A \& B \& C$ with all equal possibilities of showing up (1/3)\\
Then we can say we are only throwing a 3 sided dice, therefore the total amount of possibilities while throwing is\\
\[3^n\]
using the analogy of undistinguishable $A$s and $ B\& C$s
our equation for $ \|A\|= \|B\|+\|C\|$
is \\
  \[ \frac{n!}{\frac{n}{3}! + \frac{2n}{3}!}\]
How many times will the sum of the number of 1's and 2's equal the
sum of the number of 3's and 4's and equal the sum of the number of
5's and 6's?  What is the probability of this occurring?

How many times will you roll a 1 twice in succession?  For the
purpose of this calculation, the sequence ...11.... counts as once,
but so does ...111....  The sequence ...1111... counts as twice.  What
is the probability of this occurring?

How many times will you roll a 1 $k$-times in succession?  As with
the previous case, when a 1 is counted as part of a $k$-sequence, it
is not counted as part of a subsequent $k$-sequence.  What
is the probability of this occurring?

You have a communications system that transmits bundles of data
from a source to a destination.  Most bundles are received correctly.
However, there is a random chance of the data in a bundle being in
error.  Roughly every $E^{th}$ bundle is in error.  If you transmit
$n$ bundles, what is the probability of two bundles in sequence being
in error?  what is the probability of $k$ bundles in sequence being in
error?

sense of whether or not your answers look correct.
\end{document}
